\textbf{Proof Reconstruction in Classical Propositional Logic}

### 2017-04-27 slides/slides.tex
[ slides ] Makefile added, and many changes.

% footer.
\setbeamercolor{headFoot}{fg=white, bg=plum!80!black}
\setbeamertemplate{footline}{
  \leavevmode%
  \hbox{%
  \begin{beamercolorbox}
    [wd=.8\paperwidth,ht=2.3ex,dp=1ex,left]{headFoot}%
    \hspace*{2ex}\insertshorttitle\hspace*{2mm}(\insertshortauthor)
  \end{beamercolorbox}%
  \begin{beamercolorbox}
    [wd=.2\paperwidth,ht=2.3ex,dp=1ex,right]{headFoot}%
    \insertframenumber{}/\inserttotalframenumber\hspace*{2ex}
  \end{beamercolorbox}}%
  \vskip 0pt%
  % \vspace*{1mm}%
}

@@

% \setbeamercolor{institute}{fg=blu}
\setbeamercolor{title}{fg=plum}
% \setbeamercolor{subtitle}{fg=blu}

@@

\title[Proof Reconstruction in Classical Propositional Logic]
  {\textbf{Proof Reconstruction in Classical Propositional Logic}
}
\subtitle{(Work in Progress)}
\date{Agda Implementors’ Meeting XXV\\
May 9-15th}
\author[Jonathan Prieto-Cubides and Andr\'es Sicard-Ram\'irez]{Jonathan Prieto-Cubides\\
(Joint work with Andr\'es Sicard-Ram\'irez)}
\institute{
Universidad EAFIT\\
Medell\'in, Colombia}
% --------------------------------------------------------------------------

@@

\begin{frame}[plain]
\titlepage
  \begin{tikzpicture}[overlay, remember picture] (eafit) at (current page.center)
    \node[xshift=0cm,yshift=0cm]
      {\includegraphics[width=0.25\textwidth]{figures/eafit}};
    \node[xshift=3cm,yshift=-2cm] (chalmers) at (current page.center)
      {\includegraphics[width=0.25\textwidth]{figures/chalmers}};
  \end{tikzpicture}
\end{frame}

@@

\begin{frame}[fragile, label=atp-conjunct]{Conjunct}{Inference Rule}
\begin{block}{conjunct}
\begin{agda}
conjunct : Prop → Prop → Prop
conjunct (φ ∧ ψ) ω with ⌊ eq φ ω ⌋ | ⌊ eq ψ ω ⌋
... | true  | _     = φ
... | false | true  = ψ
... | false | false = conjunct φ ω
conjunct φ ω        = φ

atp-conjunct
  : ∀ {Γ} {φ}
  → (ω : Prop)
  → Γ ⊢ φ
  → Γ ⊢ conjunct φ ω
\end{agda}
\end{block}
\end{frame}

@@

\begin{tikzpicture}
\only<1->{ \node(agdafile) at (0,0){
  \includegraphics[scale=0.8]{figures/agda-pragmas}}};
\only<1>{
  \node[fill=aliceblue, rectangle, right = 2.5cm of agdafile] (atp-pragmas){
  \scalebox{0.7}{\usebox\agdapragma}
  }
  };

>>>>

% footer.
\setbeamercolor{headFoot}{fg=white, bg=plum!80!black}
\setbeamertemplate{footline}{
  \leavevmode%
  \hbox{%
  \begin{beamercolorbox}
    [wd=.8\paperwidth,ht=2.3ex,dp=1ex,left]{headFoot}%
    \hspace*{2ex}\textbf\insertshorttitle\hspace*{2mm}|\hspace*{2mm}\textbf\insertshortauthor
  \end{beamercolorbox}%
  \begin{beamercolorbox}
    [wd=.2\paperwidth,ht=2.3ex,dp=1ex,right]{headFoot}%
    \insertframenumber{}/\inserttotalframenumber\hspace*{2ex}
  \end{beamercolorbox}}%
  \vskip 0pt%
  % \vspace*{1mm}%
}

@@

% \setbeamercolor{institute}{fg=blu}
\setbeamercolor{title}{fg=plum!80!black}
% \setbeamercolor{subtitle}{fg=blu}

@@

\title[Proof Reconstruction in Classical Propositional Logic]
  {\textbf{Proof Reconstruction in Classical Propositional Logic}
}
\subtitle{(Work in Progress)}
\date{Agda Implementors’ Meeting XXV\\
May 9-15th}
\author[Jonathan Prieto-Cubides and Andr\'es Sicard-Ram\'irez]{Jonathan Prieto-Cubides\\
Joint work with Andr\'es Sicard-Ram\'irez}
\institute{
Universidad EAFIT\\
Medell\'in, Colombia}
% --------------------------------------------------------------------------

@@

\begin{frame}[plain]
\titlepage
  \begin{tikzpicture}[overlay, remember picture]
   \tikzset{shift={(current page.center)}}
    \node[xshift=-4.5cm,yshift=-3.5cm] (eafit)
      {\includegraphics[width=0.2\textwidth]{figures/eafit}};
    \node[xshift=4.5cm,yshift=-3cm] (chalmers)
      {\includegraphics[width=0.18\textwidth]{figures/chalmers}};
  \end{tikzpicture}
\end{frame}

@@

\begin{frame}[fragile, label=atp-conjunct]{Conjunct}{Inference Rule}
\begin{itemize}
\item In \hyperlink{tstp-syntax}{TSTP}
\begin{tptp}
\end{tptp}
\item Function:
\begin{agda}
conjunct : Prop → Prop → Prop
conjunct $(φ \wedge ψ)$ $ω$ with $⌊$ eq $φ$ $ω$ $⌋$ | $⌊$ eq ψ $ω$ $⌋$
... | true  | _     = $φ$
... | false | true  = $ψ$
... | false | false = conjunct $φ$ $ω$
conjunct $φ$ $ω$       = $φ$
\end{agda}
\item Theorem
\begin{agda}
atp-conjunct
  : ∀ $\{Γ\}$ $\{φ\}$
  → $(ω : Prop)$
  → $Γ \vdash φ$
  → $Γ \vdash$ conjunct $φ$ $ω$
\end{agda}
\end{itemize}
\end{frame}

@@

\begin{tikzpicture}
\only<1->{ \node(agdafile) at (0,0){
  \includegraphics[scale=0.8]{figures/agda-pragmas}}};
\only<1>{
  \node[fill=aliceblue, rectangle, right = 2.5cm of agdafile] (atp-pragmas){
  \scalebox{0.9}{\usebox\agdapragma}
  }
  };
